% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={collaboration},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\title{collaboration}
\author{}
\date{}

\begin{document}
\maketitle

\section{Identity2}

\begin{verbatim}
 ┌─┐┌┬┐┌─┐┬   ┌─┐┬ ┬┌┬┐┬ ┬┌─┐┌─╮┬┬ ┬┌─┐
 └─┐││││ ││   ├─┤│ │ │ ├─┤│ │├┐┘││╲││┌┐
 └─┘┴ ┴└─┘└─┘ ┴ ┴└─┘ ┴ ┴ ┴└─┘╵ ┴┴┴ ┴└─┘
\end{verbatim}

\subsection{Collaboration}

\begin{quote}
If you are an established writer you have established your support
network. If not, consider some of the following.
\end{quote}

\subsubsection{Critique Circle}

\textbf{www} Critique Circle

This what they say about themselves:

\begin{itemize}
\item
  Improve your writing skills in one of the largest and longest-running
  writing communities on the web.
\item
  Vibrant writing community thousands of writers working together to
  improve their writing.
\item
  It's all about reciprocity. Critique the stories of others and in turn
  they will crit your stories.
\item
  Active forums. Discussion groups on nearly any topic under any sun.
\item
  Continuously improve your writing by critting the works of others and
  building relationships with other authors who will help you with your
  own manuscript.
\item
  Membership is free and always has been. There is also a premium
  subscription that you can buy.
\item
  Stories submitted to CC are not considered 'published online' and
  cannot be found on search engines.
\end{itemize}

\subsubsection{Wordtune}

\textbf{www} Wordtune

\begin{itemize}
\item
  Wordtune was built by AI21 Labs, founded in 2018 by AI luminaries. Our
  goal is to revolutionize the way we read and write.
\item
  We design advanced AI tools and language models that understand the
  context and semantics of written text.
\item
  These models are what set Wordtune apart as the first AI-based writing
  companion, moving far beyond grammar and spelling fixes to help you
  put your own thoughts into written words.
\end{itemize}

\subsubsection{Xlibris}

\textbf{www} Xlibris

\begin{itemize}
\tightlist
\item
  Publishing Packages, Editorial Services, Add-On Services, and
  Marketing Services
\end{itemize}

\subsubsection{Writing Forums}

\textbf{www} Writing Forums

\begin{itemize}
\tightlist
\item
  Writing Elements -Character Development - Word Mechanics - Creative
  Process - Style - General Writing - Editing - Publishing -
  Self-Publishing - Issues Writers Face - Motivation - Interviews.
\end{itemize}

\subsubsection{Wikibooks}

\textbf{www} Wikibooks

\begin{itemize}
\item
  The open-content textbooks collection that anyone can edit.
\item
  One web page for every book ever published. It's a lofty but
  achievable goal.
\item
  To build Open Library, we need hundreds of millions of book records, a
  wiki interface, and lots of people who are willing to contribute
  theirtime and effort to building the site.
\item
  To date, we have gathered over 20 million records from a variety of
  large catalogs as well as single contributions, with more on the way.
  3,465 books with 94,640 pages.
\end{itemize}

\subsubsection{Mobileread}

\textbf{www} Mobileread

\begin{itemize}
\tightlist
\item
  ebooks and forums
\end{itemize}

\subsubsection{NaNoWriMo}

\textbf{www} NaNoWriMo

\begin{itemize}
\item
  National Novel Writing Month began in 1999 as a daunting but
  straightforward challenge: to write 50,000 words of a novel during the
  thirty days of November.
\item
  Now, each year on November 1, hundreds of thousands of people around
  the world begin to write, determined to end the month with 50,000
  words of a brand-new novel. You may know this mass creative explosion
  by the name National Novel Writing Month, or NaNoWriMo---but that's
  not all that NaNoWriMo is!
\item
  NaNoWriMo believes in the transformational power of creativity. We
  provide the structure, community, and encouragement to help people
  find their voices, achieve creative goals, and build new worlds---on
  and off the page.
\end{itemize}

\subsubsection{Open Library}

\textbf{www} Open Library

\begin{itemize}
\item
  Open Library is an initiative of the Internet Archive, building a
  digital library of Internet sites and other cultural artifacts in
  digital form.
\item
  Other projects include the Wayback Machine, archive.org and
  archive-it.org
\item
  One web page for every book ever published. It's a lofty but
  achievable goal.
\item
  To build Open Library, we need hundreds of millions of book records, a
  wiki interface, and lots of people who are willing to contribute their
  time and effort to building the site.
\item
  To date, we have gathered over 20 million records from a variety of
  large catalogs as well as single contributions, with more on the way.
\end{itemize}

Spell check your entire html site

\begin{verbatim}
       ┬                   ┌─┐  ┌─┐        
       │┌┬┐┌─┐┬ ┬┌┬┐┬┌┬┐┬ ┬╵ │  │ ╵┌─┐┌┬┐  
       │ ││├┤ │╲│ │ │ │ └┬┘┌─┘○ │  │ ││││  
       ┴ ┴┘└─┘┴ ┴ ┴ ┴ ┴  ┴ └──  └─┘└─┘┴ ┴   
\end{verbatim}

\end{document}
