% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={print-on-demand},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\title{print-on-demand}
\author{}
\date{}

\begin{document}
\maketitle

\begin{verbatim}
 ┌─┐┌┬┐┌─┐┬    ┌─╮ ┌─┐ ┌┬┐
 └─┐││││ ││    ├─┘ │ │  ││
 └─┘┴ ┴└─┘└─┘  ┴ ○ └─┘○ ┴┘ ○
\end{verbatim}

Back to Home

Wikipedia article

\subsection{Indie publisher}

Also called "small press" and "Independent press", are publishers rather
than printers, if that is still a distinction?, this subject will get a
chapter in time.

\subsection{Print-on-demand: fees and royalties.}

As an example Kindle Direct Publishing charges nothing to place your
book in the storefront, but they share profits. When I last checked the
author gets 60\% in royalties (whats made on the sale) for normal
distribution and 40\% for expanded.

Ingramspark has lower royalties and a US\$49 setup fee to upload a
title.

Companies will offer pricing calculators.

Amazon competes at retail so Ingramspark may be more attractive if you
are targeting stores.

My point is the options vary so be clear about your objectives and
research thoroughly.

If you can make this decision early you may avoid rework be designing
you product to the market place you are entering.

Some companies also offer print on demand in conjunction with packages
that you have to buy first. These tend to be the pricier options.
Bookbaby, for example, charges \$399 for their package which allows
distribution on sites like Amazon.

Where there is an online calculator I have priced a 84 page 8.5" x 5.5",
or as near as I can find, Perfect bound B\&W on basic paper, which I
present in a table like below. Please do you own test this is mid 2022,
this will date.

\begin{verbatim}
  ╭──────────────────────────────────────────────╮ 
  │ copies │ pages │    $total   │  $each  │ Frt | 
  ╰──────────────────────────────────────────────╯ 
\end{verbatim}

\subsection{Non-exhaustive list of P.O.D. untested, not recommendations}

\textbf{www} Ingram Lightning Source

\begin{quote}
Upload your titles to Lightning Source. Titles are made available to our
global book distribution network. Customers order your titles---online
or in stores. Lightning Source prints only those books. You choose if
books are shipped direct to you or your customers.
\end{quote}

One of the more popular print on demand companies. Connected to over
40,000 retailers, libraries, and e-commerce outlets. Also does eBooks
version. Some options for formatting and some customizability.

\textbf{www} Draft 2 Digital

\begin{quote}
We are Self-Publishing with Support Your book is your priority. Our
priority is you. We build tools and services that let you focus on
writing while we take care of layout, publishing, distribution,
print-on-demand paperbacks, and more. Keep writing. We're here for the
rest.
\end{quote}

\textbf{www} Acutrack

\begin{quote}
Print \& Sell Your Book Worldwide. Profitably. With us, you can print
your book and sell it globally with instant shipping -- it's an enormous
improvement over the one-at-a-time print-on-demand (POD) model. We'll
have your books out the door before a POD company adds a print order
into its system.
\end{quote}

Acutrack allows authors to work with their pre-press team to finalize
your product before it goes to print. They offer a variety of different
options for your book and they let you order anywhere from 1-1000 copies
at a time, making the process super customizable. They also integrate
the book into whatever storefront you use, allowing for easier
distribution.

\textbf{www} Kindle Direct Publishing

\begin{quote}
Self-publish eBooks and paperbacks for free with Kindle Direct
Publishing, and reach millions of readers on Amazon. Get to market fast.
Publishing takes less than 5 minutes and your book appears on Kindle
stores worldwide within 72 hours. Make more money. Earn up to 70\%
royalty on sales to customers in the US, Canada, UK, Germany, India,
France, Italy, Spain, Japan, Brazil, Mexico, Australia and more. Enroll
in KDP Select and earn more money through Kindle Unlimited and the
Kindle Owners' Lending Library. Keep control. Keep control of your
rights and set your own list prices. Make changes to your books at any
time. Publish in digital and print. Publish Kindle eBooks and paperbacks
for free on KDP. Get started today! Self-publish with KDP for free.
Learn how easy it is.
\end{quote}

Very popular and widely-used print on demand publisher, its extremely
user-friendly. Comes with a free ISBN which allows you to use their
Expanded Distribution Network, meaning other companies like stores and
schools can order your book. Delivered in 24 to 48 hours.

\textbf{www} Lulu

\begin{quote}
Publish. Print. Prosper. Publish, print, and sell your books globally
with our Print-On-Demand network while eliminating the risk and hassle
of inventory and fulfillment.
\end{quote}

Lulu prints hardcover books as well as paperback and offer a huge
variety of book formats, like yearbooks, comics, or novels. Authors can
make their books more personalized, and it gives the author more
control. You'll be able to sell on Amazon, but it takes a little longer
for Lulu to get your book ready than Amazon does.

\begin{verbatim}
  ╭──────────────────────────────────────────────╮ 
  │ copies │ pages │    $total   │  $each  │ Frt | 
  │      1 │    84 │     US$3.83 │ US$3.83 │  x  | 
  ╰──────────────────────────────────────────────╯ 
\end{verbatim}

\textbf{www}

\begin{quote}
Where Writers Become Authors Print and self-publish your own book today.
At BookBaby, we provide every \textgreater{} service you need, all under
one roof.
\end{quote}

May be better for authors with an established platform and some cash to
invest in their production. The cost is higher than other platforms, and
print-to-order is after an initial order of 25 books.

\begin{verbatim}
  ╭──────────────────────────────────────────────╮ 
  │ copies │ pages │    $total   │  $each  │ Frt | 
  │     25 │    84 │   US$292.75 │US$11.71 │  x  | 
  │    100 │    84 │   US$619.00 │ US$6.19 │  x  | 
  │   1000 │    84 │ US$4,049.00 │ US$4.05 │  x  | 
  ╰──────────────────────────────────────────────╯ 
\end{verbatim}

\textbf{www} The Book Patch

\begin{quote}
Self Publishing Simplified, No Minimum Orders, Best Printing Prices, 3-5
Business Day Turnaround, No Setup Fee, Zero Fee Bookstore
\end{quote}

Advertises no setup or listing fees and charges on the number of books
ordered. The more you buy, the cheaper per book. You also could keep all
of your royalties, good option if the fees on Lulu or KDP are a
deterrent.

\begin{verbatim}
  ╭──────────────────────────────────────────────╮ 
  │ copies │ pages │    $total   │  $each  │ Frt | 
  │     25 │    84 │   US$129.75 │ US$5.19 │  x  | 
  │    100 │    84 │   US$441.00 │ US$4.41 │  x  | 
  │   1000 │    84 │ US$3,630.00 │ US$3.63 │  x  | 
  ╰──────────────────────────────────────────────╯ 
\end{verbatim}

\textbf{www} Blurb

\begin{quote}
WHAT WILL FILL YOUR PAGES? Adventure and exploration were made to be
documented. Turn your journey into a professional-quality photo book.
\end{quote}

There are fees to sell through sites like Amazon, but you can sell on
Blurb for free. They allow some control over the profit margins on each
sale.

\begin{verbatim}
  ╭──────────────────────────────────────────────╮ 
  │ copies │ pages │  discount   │   each  │ Frt | 
  │      1 │    84 │1 - 1 bks-10%│  £17.76 │  x  | 
  │  10-19 │    84 │10-19 bks-10%│         │  x  |
  │  20-49 │    84 │20-49 bks-20%│         │  x  |
  │    100 │    84 │50+   bks-25%│         │  x  | 
  │   1000 │    84 │50+   bks-25%│         │  x  | 
  ╰──────────────────────────────────────────────╯ 
\end{verbatim}

\textbf{www} Trafford Publishing

\begin{quote}
Do You Have a Story to Tell? Trafford Publishing has helped over 17,000
writers publish their books since 1995. Achieve your dream of becoming
an author with all the publishing, marketing, and bookselling tools you
need.
\end{quote}

Option for authors with a little more cash to invest. They offer
printing if you buy one of their packages. For the up-front cost, you're
getting a very polished product.

\textbf{www} Diggy POD

\begin{quote}
Self Publishing We are the go to online resource for the
do-it-yourselfer that wants to learn about the self-publishing process.
\end{quote}

Print books in batches of 24, and have a pricing calculator on their
website. They offer free shipping over 100.

I did a test quote for the blue book shown in the image on the home page
of ths site.

\begin{verbatim}
  ╭──────────────────────────────────────────────╮ 
  │ copies │ pages │    $total   │  $each  │ Frt | 
  │     24 │    84 │   US$177.05 │ US$7.38 │  x  | 
  │    100 │    84 │   US$367.23 │ US$3.67 │  x  | 
  │   1000 │    84 │ US$2,083.47 │ US$2.08 │  x  | 
  ╰──────────────────────────────────────────────╯ 
\end{verbatim}

\textbf{www} Espresso Book Machine®

\begin{quote}
Books Printed In Minutes At Point Of Sale For Immediate Pick Up Or
Delivery
\end{quote}

Allow you to collaborate with editors and designers, but it allows
stores and libraries to print books in-house using special printers.
This basically takes out the middle man, or a retailer, and brings the
book directly to the library or school ordering the book.

\textbf{www} 48hr Books

48hr Books Pdf Howto

48hr Books Printed Howto (USA)

Like the name implies, 48hr Books gets your book ready to go between
twenty-four and forty-eight hours. They have the option to print
hardcover, and they have templates for authors to use if they're unable
to get their own formatting done. However, this company does require
authors to order a minimum of ten books, which means it isn't
technically print-on-demand in the literal sense.

\begin{verbatim}
  ╭──────────────────────────────────────────────╮ 
  │ copies │ pages │    $total   │  $each  │ Frt | 
  │     24 │    84 │   US$176.69 │ US$7.36 │  x  | 
  │    100 │    84 │   US$356.20 │ US$2.85 │  x  | 
  │   1000 │    84 │ US$2,109.70 │ US$2.06 │  x  | 
  ╰──────────────────────────────────────────────╯ 
\end{verbatim}

\subsubsection{China/H.K. suppliers}

Candidus Print

Candidus Novel

http://www.candidusprint.com - +86-755-33073344 (WhatsApp -
+86-13510244214) Skype: uuuhy@msn.com / rainbowprinting QQ: 446504458
WeChat: he-yong99

\begin{verbatim}
  ╭──────────────────────────────────────────────╮ 
  │ copies │ pages │    $total   │  $each  │ Frt | 
  │    100 │    84 │   US$260.00 │ US$2.60 │  x  | 
  ╰──────────────────────────────────────────────╯ 
\end{verbatim}

http://www.gpp.com.hk/bookpublishing/index.htm \textbf{www} Green Pagoda
Press P.O.D.

\begin{quote}
It is easy to publish your book for the first timer. With one click,
your book is printed.You can upload your final proofread manuscript or
send us a PDF for output. If you have not formatted your manuscript, our
design team can help you with the artwork, translation and cover design.
Your ISBN, if you have one. We recommend that you obtain an ISBN before
you publish as your ISBN should appear on the copyright page.
\end{quote}

\end{document}
